---
title: "Developing Data Products Week 3 Assignment"
author: "John Paul Sanglay"
date: "January 25, 2019"
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F,message=F,warning=F)
```

## Introduction

### Objective

The objective of the assignment is to create web page presentation using R Markdown that features an interactive plot created with Plotly.

### **Data**

Data is derived from the built-in 'ChickWeight' data set in R. It comprises of 578 rows and 4 columns from an experiment on the effect of diet on early growth of chicks. The data is then processed before plotting to determine the chicks with the highest increase in body weight per diet.

## **Interactive Plot**

```{r ChickWeight}
library(plotly)
library(plyr)
df <- ChickWeight
zero.weight <- df[df$Time==0,]$weight
ratio <- function(x,y){
        A <- x/zero.weight[as.numeric(as.character(y))]
        return(A)
}
Increase <- mapply(ratio,df$weight,df$Chick)
df <- cbind(df,Increase)
max.Inrease <- ddply(df,~Diet,subset,Increase==max(Increase),select=c('Diet','Increase','Chick'))$Chick
plot_ly(x=subset(ChickWeight,Chick==max.Inrease[1])$Time,mode="lines+markers") %>%
        add_trace(y=subset(ChickWeight,Chick==max.Inrease[1])$weight,name="Diet 1") %>%
        add_trace(y=subset(ChickWeight,Chick==max.Inrease[2])$weight,name="Diet 2") %>%
        add_trace(y=subset(ChickWeight,Chick==max.Inrease[3])$weight,name="Diet 3") %>%
        add_trace(y=subset(ChickWeight,Chick==max.Inrease[4])$weight,name="Diet 4") %>%
        layout(title = "Growth of Chicks on Different Diets",
         xaxis=list(title="Time (day)"),
         yaxis=list (title="Body Weight (g)"))
```

***
THANK YOU
